Alex's Notes and Text Fragments for the JSS Manuscript

### 2023-12-25 paper/article.Rmd
align figures

```{r knndm-eval, fig.cap='Leave-one-block-out CV based on $k$-means clustering of the coordinates as implemented in package \\pkg{sperrorest} (method `"spcv\\_coords"` in \\pkg{mlr3spatiotempcv}).', out.width="55%", fig.pos="ht", echo=FALSE}
rsmp_coords = rsmp("spcv_coords", folds = 5)

@@

autoplot(rsmp_block_systematic,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE, label_size = 4) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(text = ggplot2::element_text(size = 16),
    plot.title = ggtext::element_textbox(size = 13,
      r = ggplot2::unit(7, "pt"),
      height = ggplot2::unit(0.46, "inch"), linewidth = 0.8)) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 1.5)))
```

@@

plot_env_single = autoplot(rsmp_env,
  size = 0.3, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(plot.title = ggtext::element_textbox(size = 8),
    axis.text = ggplot2::element_text(size = 7),
    legend.title = ggtext::element_textbox(size = 8),
    legend.text = ggtext::element_textbox(size = 6),
    legend.key.size = ggplot2::unit(0.4, "cm"))

plot_env_multi = autoplot(rsmp_env_multi,
  size = 0.3, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(plot.title = ggtext::element_textbox(size = 8),
    axis.text = ggplot2::element_text(size = 7),
    legend.title = ggtext::element_textbox(size = 8),
    legend.text = ggtext::element_textbox(size = 6),
    legend.key.size = ggplot2::unit(0.4, "cm"))

@@

```{r vis-spcv-eval, fig.cap="Spatial leave-one-block-out partitioning using coordinate-based clustering to create roughly equally sized polygonal blocks. Due to space limitations only the first two folds of the first repetition are shown.", fig.pos="ht", out.width="100%", echo=FALSE}
autoplot(rsmp_sp, task, fold_id = 1:2, size = 0.3) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) *
  ggplot2::theme(plot.title = ggtext::element_textbox(size = 8),
    axis.text = ggplot2::element_text(size = 7),
    legend.title = ggtext::element_textbox(size = 8),
    legend.text = ggtext::element_textbox(size = 7),
    legend.key.size = ggplot2::unit(0.4, "cm"))
```

@@

```{r vis-nspcv-eval, fig.cap="Random (non-spatial) four-fold CV partitioning. Only the first two folds of the first repetition are shown.", out.width="100%", fig.pos="ht", echo=FALSE}
autoplot(rsmp_nsp, task, fold_id = 1:2, size = 0.3) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) *
  ggplot2::theme(plot.title = ggtext::element_textbox(size = 8),
    axis.text = ggplot2::element_text(size = 7),
    legend.title = ggtext::element_textbox(size = 8),
    legend.text = ggtext::element_textbox(size = 7),
    legend.key.size = ggplot2::unit(0.4, "cm"))
```

>>>>

```{r knndm-eval, fig.cap='Leave-one-block-out CV based on $k$-means clustering of the coordinates as implemented in package \\pkg{sperrorest} (method `"spcv\\_coords"` in \\pkg{mlr3spatiotempcv}).', out.width="60%", fig.pos="ht", echo=FALSE}
rsmp_coords = rsmp("spcv_coords", folds = 5)

@@

autoplot(rsmp_block_systematic,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE, label_size = 4) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(text = ggplot2::element_text(size = 15),
    plot.title = ggtext::element_textbox(size = 12,
      r = ggplot2::unit(7, "pt"),
      height = ggplot2::unit(0.46, "inch"), linewidth = 0.8)) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 1.5)))
```

@@

plot_env_single = autoplot(rsmp_env,
  size = 0.3, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(plot.title = ggtext::element_textbox(size = 8,
    r = ggplot2::unit(4, "pt"),
    height = ggplot2::unit(0.30, "inch"), linewidth = 0.5),
  axis.text = ggplot2::element_text(size = 8.5),
  legend.title = ggtext::element_textbox(size = 10),
  legend.text = ggtext::element_textbox(size = 8),
  legend.key.size = ggplot2::unit(0.4, "cm")) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 0.8)))

plot_env_multi = autoplot(rsmp_env_multi,
  size = 0.3, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(plot.title = ggtext::element_textbox(size = 8,
    r = ggplot2::unit(4, "pt"),
    height = ggplot2::unit(0.30, "inch"), linewidth = 0.5),
  axis.text = ggplot2::element_text(size = 8.5),
  legend.title = ggtext::element_textbox(size = 10),
  legend.text = ggtext::element_textbox(size = 8),
  legend.key.size = ggplot2::unit(0.4, "cm")) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 0.8)))

@@

```{r vis-spcv-eval, fig.cap="Spatial leave-one-block-out partitioning using coordinate-based clustering to create roughly equally sized polygonal blocks. Due to space limitations only the first two folds of the first repetition are shown.", fig.pos="ht", out.width="100%", echo=FALSE}
autoplot(rsmp_sp, task, fold_id = 1:2, size = 0.3) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) *
  ggplot2::theme(plot.title = ggtext::element_textbox(size = 8,
    r = ggplot2::unit(4, "pt"),
    height = ggplot2::unit(0.30, "inch"), linewidth = 0.5),
  axis.text = ggplot2::element_text(size = 8.5),
  legend.title = ggtext::element_textbox(size = 10),
  legend.text = ggtext::element_textbox(size = 8),
  legend.key.size = ggplot2::unit(0.4, "cm")) *
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 0.8)))
```

@@

```{r vis-nspcv-eval, fig.cap="Random (non-spatial) four-fold CV partitioning. Only the first two folds of the first repetition are shown.", out.width="100%", fig.pos="ht", echo=FALSE}
autoplot(rsmp_nsp, task, fold_id = 1:2, size = 0.3) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) *
  ggplot2::theme(plot.title = ggtext::element_textbox(size = 8,
    r = ggplot2::unit(4, "pt"),
    height = ggplot2::unit(0.30, "inch"), linewidth = 0.5),
  axis.text = ggplot2::element_text(size = 8.5),
  legend.title = ggtext::element_textbox(size = 10),
  legend.text = ggtext::element_textbox(size = 8),
  legend.key.size = ggplot2::unit(0.4, "cm")) *
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 0.8)))
```
